

\cvsection{Achievements}

\cvachievement{\faTrophy}{Ranking Second in UniversityHack 2018 DATATHON}{UniversityHack 2018 DATATHON is a Spanish national contest where only students can participate (from Bachelor level to Phd). The goal for the competition was to predict the purchasing power of a client, using data provided by Spanish bank Cajamar. }
\cvtag{Leadership} 
\cvtag{Teamwork}
\divider

\cvachievement{\faUsers}{Open source contributions}{}

\cvtag{Sklearn}
\cvtag{Facebook Prophet}
\cvtag{Pytorch Audio}
\cvtag{Jupyter Lab}
\divider

\cvachievement{\faUsers}{Coach at Openhack - Coding for humanity}{Coached two hackathon events for Openhack, a non-porfit organization looking to making a difference through open source development}


\cvsection{Tools}

\textcolor{SlateGrey}{\textbf{Internet Of Things}}
\newline

\begin{itemize}
    \item Raspberry PI home assistant setup.
    \item Microsoft Azure IoT setup.
\end{itemize}

\textcolor{SlateGrey}{\textbf{Deep learning libraries}}
\newline

\begin{itemize}
    \item Advance use of Pytorch, Pytorch lightning. Profiling and serving with ONNX standar
    \item Medium knowledge of Tensorflor 1.X, basic 2.X.
\end{itemize}

\textcolor{SlateGrey}{\textbf{Cloud Providers}}
\newline

\begin{itemize}
    \item Advanced Google Cloud. Server setup (web hosting, Cloud hosting, Restful API, Redis, SQL ..). Online model serving and kubertenes cluster management.
    \item Medium knowledge of Azure ecosystem: functions, devops.
    \item Basic AWS.
\end{itemize}

\textcolor{SlateGrey}{\textbf{Software (Frontend)}}
\newline

\begin{itemize}
    \item Basic HTML and javascript knowledge, my top work is at my personal page jiwidi.me.
\end{itemize}




\cvsection{Other Interests}

\cvtag{Photography}
\cvtag{Open source}
\cvtag{Nature}

