


\cvsection{Projects}

\textcolor{SlateGrey}{\textbf{\href{https://github.com/jiwidi/las-pytorch}{\faGithub \, LAS-Pytorch }}} \\ 
Implementation of Listen, Attend and spell model for E2E ASR.
\newline
\vspace{1pt}


\textcolor{SlateGrey}{\textbf{\href{https://github.com/jiwidi/time-series-forecasting-with-python}{\faGithub \,  Time series with Python  }}} \\ 
A use-case focused tutorial for time series forecasting with Python.
\newline
\vspace{1pt}


\textcolor{SlateGrey}{\textbf{\href{https://github.com/jiwidi/jupyter-lab-docker-rpi}{\faGithub \, Jupyter-lab-docker-rpi}}} \\ 
A Docker image to run jupyterlab on your raspberry pi. 
\newline
\vspace{1pt}


\textcolor{SlateGrey}{\textbf{\href{https://github.com/jiwidi/DeepSpeech-pytorch}{\faGithub \, DeepSpeech-pytorch}}} \\ 
Pytorch code for DeepSpeech 2.0.
\newline
\vspace{1pt}



\textcolor{SlateGrey}{\textbf{\href{https://github.com/jiwidi/Netflix-RNN-Recommender}{\faGithub \, Netflix-RNN-Recommender}}} \\ 
Implicit recommender for Netflix dataset.
\newline
\vspace{1pt}

\textcolor{SlateGrey}{\textbf{\href{https://github.com/jiwidi/gmm-classifier}{\faGithub \, GMM-Classifier}}} \\ 
Python implementation for a Gaussian mixture model classifier.
\newline
\vspace{1pt}

\textcolor{SlateGrey}{\textbf{\href{https://github.com/jiwidi/PLS-regression-tensorflow}{\faGithub \, PLS Regression Tensorflow}}} \\ 
PLS regression in TensorFlow 2.0.
\newline
\vspace{1pt}

\textcolor{SlateGrey}{\textbf{\href{https://github.com/jiwidi/DailyQwertee}{\faGithub \, Daily Qweerte}}} \\ 
Bot that sends you new shirts from qweerte.com. Deployed in GCP since 2015 with 180 users.
\newline
\vspace{1pt}


\cvsection{Tools}

% \textcolor{SlateGrey}{\textbf{Internet Of Things}}
% \newline

% \begin{itemize}
%     \item Raspberry PI home assistant setup.
%     \item Microsoft Azure IoT setup.
% \end{itemize}

\textcolor{SlateGrey}{\textbf{Machine learning libraries}}
\newline

\begin{itemize}
    \item Advance use of Pytorch, Pytorch lightning, Sklearn, FB Prophet. Profiling and serving with ONNX standard.
    \item Medium knowledge of Tensorflow 1.X, basic 2.X.
\end{itemize}

\textcolor{SlateGrey}{\textbf{Cloud Providers}}
\newline

\begin{itemize}
    \item Advanced Google Cloud. Server setup (BigQuery, Cloud hosting, Restful API, Redis, Cloud composer, SQL ..).
    \item Medium knowledge of Azure ecosystem: functions, devops.
    \item Basic AWS.
\end{itemize}

\textcolor{SlateGrey}{\textbf{Software (Frontend)}}
\newline

\begin{itemize}
    \item Basic HTML and javascript knowledge, my top work is at my personal page jiwidi.me.
\end{itemize}

\textcolor{SlateGrey}{\textbf{Software (Backend)}}
\newline

\begin{itemize}
    \item Kubernetes, Docker, Apache webserver
    \item Databases: Django, PostgreSQL, MySQL. 
\end{itemize}

\cvsection{Achievements}


\textcolor{SlateGrey}{\textbf{Ranking Second in UniversityHack 2018 DATATHON}}: \\ Biggest spanish data science competition.
\newline


\vspace{1pt}

\textcolor{SlateGrey}{\textbf{Open source contributions}} \\ Sklearn, Facebook Prophet, Pytorch Audio, Jupyter Lab.
\newline


\vspace{1pt}

\textcolor{SlateGrey}{\textbf{Coach at Openhack - Coding for humanity}} \\ Coached two hackathon events for Openhack, a non-porfit organization.


\cvsection{Other Interests}

\cvtag{Photography}
\cvtag{Open source}
\cvtag{Nature}
\cvtag{Cycling}
\cvtag{Custom keyboards}