%-------------------------------------------------------------------------------
%	SECTION TITLE
%-------------------------------------------------------------------------------
\cvsection{Work Experience}


%-------------------------------------------------------------------------------
%	CONTENT
%-------------------------------------------------------------------------------
\begin{cventries}

%---------------------------------------------------------
\cventry
    {Co-Founder - Head of AI} % Job title
    {EcomID} % Organisation
    {Stockholm based} % Location
    {November 2023 - Present} % Date(s)
    {
        \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Leads the AI/ML function at eComID, shaping company strategy and product roadmap as a key decision maker, defining technical direction and closely collaborating with cross-functional leadership to drive product design and user experience.}
        \item {Designed end-to-end AI architecture: data pipelines, model training infrastructure, and production deployment systems.}
        \end{cvitems}
    }

\cventry
    {Founder Engineer} % Job title
    {Shaped.ai} % Organisation
    {Remote, New York} % Location
    {April 2022 - November 2023} % Date(s)
    {
        \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Developed and deployed machine learning models and infrastructure enabling +50 customers to build real-time recommendation systems.}
        \item {Built and deployed semantic search systems leveraging recommendation model representations.}
        \item {Designed and implemented real-time feature-store and data ingestion pipelines, minimizing train-inference disparities by merging batch and streaming pipelines.}
        \end{cvitems}
    }

\cventry
    {Senior Machine Learning Engineer}
    {H\&M}
    {Stockholm, Sweden}
    {Feb 2020 - April 2022}
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Organized H\&M's inaugural Kaggle competition, involving over 2,900 international teams and a prize fund of \$50,000.}
        \item {Engineered neural-based recommendation systems, significantly boosting customer engagement, revenue, and online interaction.}
        \item {Designed and implemented infrastructure on GCP for real-time recommendation model serving. Reduced ingestion time of user events from 16 hours to 3 seconds.}
        \item {Steered A/B tests, experimentation, and established feedback mechanisms for internal dashboards.}
        \end{cvitems}
    }

\cventry
    {Data Scientist}
    {Sandvik}
    {Stockholm, Sweden}
    {Oct 2018 - Feb 2020}
    {
        \begin{cvitems}
            \item {Developed abnormal behavior models for multivariate distributions in high-performance industrial processes.}
            \item {Deployed and maintained inference servers on GCP.}
        \end{cvitems}
    }

\cventry
    {Data Scientist}
    {Polystar group}
    {Stockholm, Sweden}
    {Oct 2017 - July 2018}
    {
        \begin{cvitems}
            \item {Developed anomaly detection models for telecommunications networks.}
        \end{cvitems}
    }

\cventry
    {Software Engineer Intern}
    {Ahora freeware}
    {Valencia, Spain}
    {Jun 2016 - Oct 2017}
    {
        \begin{cvitems}
            \item {Designed a cloud-based library integrating with existing CRM for file storage across Dropbox, Office365, and Google Drive.}
        \end{cvitems}
    }


\end{cventries}
