%-------------------------------------------------------------------------------
%	SECTION TITLE
%-------------------------------------------------------------------------------
\cvsection{Open Source work}

{\textbf{\href{https://github.com/scikit-learn/scikit-learn}{\faGithub \, Sklearn }}} \\ Several improvements to the Partial Least Squares (PLS) implementation and helper methods. 

{\textbf{\href{https://github.com/pytorch/audio}{\faGithub \, Pytorch Audio }}} \\ Added new baseline datasets (Tedlium 1, Tedlium 2, Tedlium 3) and code to facilitate reproducible experiments over one of the most famous ASR benchmarks. 

{\textbf{\href{https://github.com/jiwidi/las-pytorch}{\faGithub \, LAS-Pytorch }}} \\ 
Open source Implementation of Listen, Attend and spell model for E2E ASR.


{\textbf{\href{https://github.com/jiwidi/Behavior-Sequence-Transformer-Pytorch}{\faGithub \, Behavior-Sequence-Transformer-Pytorch }}} \\ 
Open source Implementation of Behavior-Sequence-Transformer, a published paper by Alibaba research that joins session and context based recommendation systems.

{\textbf{\href{https://www.kaggle.com/competitions/h-and-m-personalized-fashion-recommendations/data}{\faGithub \, H\&M Recommendation dataset }}} \\ 
Released an open source recommendation dataset along with the hosted Kaggle competition.



{\textbf{\href{https://github.com/jiwidi/MASTER_THESIS/blob/master/thesis.pdf}{\faGithub \,  Neural recommender systems at H\&M  }}} \\ 
Master Thesis (Cum-laude graded) for Neural based recommender at H\&M. Proposed models replaced existing ones in production.



{\textbf{\href{https://github.com/jiwidi/time-series-forecasting-with-python}{\faGithub \,  Time series with Python  }}} \\ 
A use-case focused tutorial for time series forecasting with Python.



{\textbf{\href{https://github.com/jiwidi/jupyter-lab-docker-rpi}{\faGithub \, Jupyter-lab-docker-rpi}}} \\ 
A Docker image to run JupyterLab on your Raspberry Pi. 




% {\textbf{\href{https://github.com/jiwidi/DeepSpeech-pytorch}{\faGithub \, DeepSpeech-pytorch}}} \\ 
% Pytorch code for DeepSpeech 2.0.
% 
% 

{\textbf{\href{https://github.com/jiwidi/Netflix-RNN-Recommender}{\faGithub \, Netflix-RNN-Recommender}}} \\ 
Implicit recommender for Netflix dataset.



{\textbf{\href{https://github.com/jiwidi/gmm-classifier}{\faGithub \, GMM-Classifier}}} \\ 
Python implementation for a Gaussian mixture model classifier.



{\textbf{\href{https://github.com/jiwidi/PLS-regression-tensorflow}{\faGithub \, PLS Regression Tensorflow}}} \\ 
PLS regression in TensorFlow 2.0.

{\textbf{\href{https://github.com/AlwaysLearningDeeper/OpenAI_Challenges}{\faGithub \, OpenAI Game Challenges}}} \\ 
My first ever project with AI where I solved the OpenAI game challenges with reinforcement learning.

% {\textbf{\href{https://github.com/jiwidi/DailyQwertee}{\faGithub \, Daily Qweerte}}} \\ 
% Bot that sends you new shirts from qweerte.com on a daily basis.


